More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-11-14 2016-Weak-FH-Bisim/WeakBisim.tex
New OT arrows

The semantics of open pNets will be defined  as an open automaton. An open
automaton is an automaton where each transition composes transitions of several LTSs with
action of some holes, the transition occurs if some predicates hold, and can involve a 
set of state modifications.
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transitions]
	\label{def:OpenTransitions}
	An \emph{open transition} over a set  $(S_i,s_{0 i}, \rightarrow_i)^{i\in
	I}$ of LTSs, a
	set $J$ of holes with sorts $\Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is 
	a structure of the form:	
	\begin{mathpar}
	\inferrule*[myfraction=\reddottedrule]
	{\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred, \Post}
	{s \xrightarrow {v}s'}
	\end{mathpar}
	Where $s, s'\in\mathcal{S}$ and for all
        $i\in I$, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the
	LTS $(S_i,s_{0 i}, \rightarrow_i)$, and $\xrightarrow{b_j}_j$
        is a transition of the hole $j$, for any action $b_j$ in the
        sort $\Sort_j$. $v$ is a variable denoting the resulting action
        of this open transition. \Pred\ is a predicate 
	over the different variables of the
	terms, labels, and states $s_i$, $b_j$, $s$, $v$. \Post\ is a set of equations that 
	hold \emph{after the open transition}, they are represented as a substitution of the 
	form $\{x_k\gets e_k\}^{k\in K}$ 
	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
	variables of the open transition.
\end{definition}

@@

 \smallskip
 $  OT_2  = \openrule{
                       0 \xrightarrow{\delta}_{C_3} 1 ~~
                            0 \xrightarrow{l}_{C_4} 0  ~~                 
                            \xrightarrow{\delta(x4)}_P ~~
                            \xrightarrow{accept(x4)}_Q 
                      }
  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
    {A1_0 \xrightarrow{\underline{\delta(x4)}} A1_1}
  $
\end{example}

@@

	\begin{description}
		\item[{\bf Tr1:}]
		$\inferrule
		{ s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
					J}\rangle} s'\in \to  }
		{ \mylangle  S,s_0, \to \myrangle
			\models
			\inferrule*[myfraction=\reddottedrule]
			{\{s \xrightarrow{\alpha}_p s'\} ,\emptyset ,
			e_b,\left\{x_j\gets e_j\right\}^{j\in J}}
			{\ostate{s} \xrightarrow{\alpha} \ostate{s'}}
		}
		$
	\end{description}
%	Note that this note is greatly simplified by the fact that variables are local to 
%	thread; introducing global state variables or accepting loops to the same 
%	state would 
%	require to reason 
%	on the scope of 
%	each variables, and to introduce additional variables to handle the several occurence 
%	of the same pLTS variable in the predicates. Indeed the constraints on pLTS 
%	transitions 
%	ensure that the same variable never appears both on the left and on the right of the 
%	equations of a predicate.

@@

	\noindent
    $\inferrule
    {k\!\in\! K \\ SV\!\!= \!{\tt clone}(SV_k) \!=\! \alpha_m^{m \in I_k\uplus J_k} \!\to\! 
    \alpha'_k \\
    	Leaves(p) \!=\! \pLTS_l^{l\in L} \\    	
    	\forall m\in I_k.
    	\pNet_m \models
    	\inferrule*[myfraction=\reddottedrule]
    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \xrightarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}}
    	%\land
    	%Leaves(\pNet_m) = \overline{pLTS}^{L_k})
    	\\
    	I' = \biguplus_{m\in I_k}\!\! I_m'
    	\\ J' = \biguplus_{m\in I_k}\!\! J'_m \uplus J_k 	\\
    	\Pred = \bigwedge_{m\in I_k}\!\! \Pred_m \land
    	\Pred_{\symb{sv}}(SV,a_i^{i\in I_k},b_j^{j\in J_k},v)\\
    	\forall j\!\!\in\!\! J_k. {\tt 
    		fresh}(b_j) \\ {\tt fresh}(v) \\ 
    	\forall i\in
    	L\backslash I'.\,s'_i=s_i 
    }
    {\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\inferrule*[myfraction=\reddottedrule]
    		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I^\prime},
    		\{\xrightarrow{b_j}_j\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_k} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \xrightarrow {v}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
    $

@@

\begin{figure}[tb]
\begin{mathpar}
  \small
  \inferrule
    {\inferrule
        {0 \xrightarrow {\delta}_{C_3} 1}
        {C_3
          \models
            \openrule{
              0 \xrightarrow {\delta}_{C_3} 1,\,
              \{\xrightarrow{\delta(x_1)}_P\},\,
              v_1=\delta(x_1)}
                      {\ostate{0}\xrightarrow{v_1}\ostate{1}}
        }\\
%      \sm{fresh}v         \\
      \inferrule%*[right={L_1}]
        {
%          \sm{fresh}{a_Q} \\
          \inferrule
              {0 \xrightarrow{l}_{C_4} 0}
              % {\ostate{0}\xrightarrow{l}\ostate{0}}
              {C_4
                \models
                \openrule{
                      0 \xrightarrow l_{C_4} 0,\,
                      \sm{Pred}_{C_4}}
                      {\ostate{0}\xrightarrow{l}\ostate{0}}
              }
        }
        {
          \textrm{Q>>R}\models
              \openrule
                  { 0 \xrightarrow {l}_{C_4} 0,\,
                    \{\xrightarrow{acc(x_2)}_Q\},\,
                    \ v_2=acc(x_2)
                  }
                  {\ostate{0}\xrightarrow{v_2}\ostate{0}}
        }   
    }
    {
     \textrm{P>>(Q>>R)}
     \models
     \openrule
         { 0 \xrightarrow{\delta}_{C_3} 1, \\ 0 \xrightarrow{l}_{C_4} 0,\\
           \{\xrightarrow{\delta(x)}_P,\,\xrightarrow{acc(x)}_Q\}, \\
            a_3=v_1 \wedge v=a_3 \wedge x_1=x_2
           }
         {\ostate{00} \xrightarrow{v} \ostate{10}}
      }\vspace{-4ex}
\end{mathpar}
  \caption{Proof of transition $OT_2$ (with interaction of processes $P$ and $Q$) for ``P>>(Q>>R)''}
  \label{usingrules:OT2}
\end{figure}

@@

 \begin{itemize}
 \item  For any open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \inferrule*[myfraction=\reddottedrule]
         {\{s^1_i\xrightarrow{a_i}_i s^{1'}_i\}^{i\in I_1}, % , s^1_i,s^{1'}_i\in 
         %States(I_1)
           \{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s^1 \xrightarrow {v} s^{1'}}

\end{mathpar}
 there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
 \begin{mathpar}
%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
    \inferrule*[myfraction=\reddottedrule]
         {\{s^{2}_i\xrightarrow{a_{i x}}_i s^{2}_{i x}\}^{i\in I_{2 x}},
           \{\xrightarrow{b_{j x}}_j\}^{j\in J_{2x}}, \Pred_{OT_x},\Post_{OT_x}}
         {s^2 \xrightarrow {v_x} s^{2}_x}
%         \right)
\end{mathpar}
 such that  $\forall x, J_1=J_{2x}, (s^{1'},s^{2}_x|\Pred_{s^{1'},s^{2}_x})\in 
 \mathcal{R}$; 
 and  \\
 $\Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j. b_j=b_{jx}  \Rightarrow \Pred_{OT_x}
     \land v\!=\!v_x \land  
     \Pred_{s^{1'},s^{2}_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
     %     \right)$.

@@

 \begin{mathpar}
 \inferrule*[myfraction=\reddottedrule]
         {\{s_i\xrightarrow{a_i}_i s'_i\}^{i\in I_1}, 
           \{\xrightarrow{b_j}_j\}^{j\in J},\Pred,\Post}
         {s \xRightarrow {v} s'}
         \in \mathcal{T}^*
 \end{mathpar}

@@

 \begin{itemize}
 \item  For any open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \inferrule*[myfraction=\reddottedrule]
         {\{s^1_i\xrightarrow{a_i}_i s^{1'}_i\}^{i\in I_1},
           \{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s^1 \xrightarrow {v} s^{1'}}

\end{mathpar}
 there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2^*$:
 \begin{mathpar}
    \inferrule*[myfraction=\reddottedrule]
         {\{s^{2}_i\xrightarrow{a_{i x}}_i s^{2}_{i x}\}^{i\in I_{2 x}},
           \{\xrightarrow{b_{j x}}_j\}^{j\in J_{2x}}, \Pred_{OT_x},\Post_{OT_x}}
         {s^2 \xRightarrow {v_x} s^{2'}_x}
\end{mathpar}
 such that  $\forall x, J_1=J_{2x}, (s^{1'},s^{2'}_x|\Pred_{s^{1'},s^{2'}_x})\in \mathcal{R}$; 
 and  \\
 $\Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j. b_j=b_{jx}  \Rightarrow \Pred_{OT_x}
     \land v\!=\!v_x \land  
     \Pred_{s^{1'},s^{2'}_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$

@@

\begin{figure}[h]
  \begin{minipage}{2cm}
  \includegraphics[width=\linewidth]{XFIG/PQR-automaton}
  \end{minipage}
  \hspace{10mm}
  \begin{minipage}{7cm}
  \begin{eqnarray*}
    OT_1 & = \openrule{0 \xrightarrow{l}_{C_3} 0
    	\\\xrightarrow{a1}_P\\ a1\neq\delta(x)}
    {\ostate{00} \xrightarrow{a1} \ostate{00}}\\
    OT_2 & = \openrule{
                       0 \xrightarrow{\delta}_{C_3} 1, ~~
                            0 \xrightarrow{l}_{C_4} 0,  ~~                 
                            \{\xrightarrow{\delta(x1)}_P, ~~
                            \xrightarrow{acc(x1)}_Q\}
                      }
                      {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}    \\
    OT_3 & = \openrule{0 \xrightarrow{l}_{C_4} 0,
                        \\1 \xrightarrow{r}_{C_3} 1,\\
                        \xrightarrow{a2}_Q,\\a2\neq\delta(x)
                        }
    {\ostate{10} \xrightarrow{a2} \ostate{10}}\\
    OT_4 & = \openrule{
                       0 \xrightarrow{\delta}_{C_4} 1, \qquad
                       1 \xrightarrow{r}_{C_3} 1, \qquad
                       \{\xrightarrow{\delta(x2)}_Q, \qquad 
                       \xrightarrow{acc(x2)}_R\} 
                       }
                      {\ostate{10} \xrightarrow{\underline{\delta(x2)}} \ostate{11}}    \\
    OT_5 & = \openrule{1 \xrightarrow{r}_{C_3} 1, \\1 \xrightarrow{r}_{C_4} 1, 
    	\\\xrightarrow{a3}_R
    	}
    {\ostate{11} \xrightarrow{a3} \ostate{11}}
    \end{eqnarray*}
  \end{minipage}
  \caption{Open Automaton for the term ``P>>(Q>>R)''}
  \label{schema:enable3bis}
\end{figure}

\begin{figure}[t]
  \begin{minipage}{2cm}
  \includegraphics[width=\linewidth]{XFIG/PQR2-automaton}
  \end{minipage}
  \hspace{10mm}
  \begin{minipage}{7cm}
  \begin{eqnarray*}
    OT'_1 & = \openrule
             {
               0 \xrightarrow{l}_{C_3} 0,~~0 \xrightarrow{l}_{C_4} 0,~~
               \{\xrightarrow{b1}_P\},~~ b1\neq\delta(y)
               }
             {\ostate{00} \xrightarrow{b1} \ostate{00}}\\
    OT'_2 & = \openrule
             {
                       0 \xrightarrow{l}_{C_5} 0, ~~
                       0 \xrightarrow{\delta}_{C_6} 1,  ~~
              \{\xrightarrow{\delta(y1)}_P,~~      \xrightarrow{acc(y1)}_Q\}~~ 
                      }
             {\ostate{00} \xrightarrow{\underline{\delta(y1)}} \ostate{01}}\\
    OT'_3 & = \openrule
             {
               0 \xrightarrow{l}_{C_5} 0,\\0 \xrightarrow{r}_{C_6} 0,
               \\ \{\xrightarrow{b2}_Q\},\\b2\neq\delta(y)
               }
    {\ostate{01} \xrightarrow{b2} \ostate{01}}\\
    OT'_4 & = \openrule
             {
                       0 \xrightarrow{\delta}_{C_5} 1, ~~
                       1 \xrightarrow{r}_{C_6} 1, ~~\{\xrightarrow{\delta(y2)}_Q, ~~
                    \xrightarrow{accept(y2)}_R\} 
                                 }
             {\ostate{01} \xrightarrow{\underline{\delta(y2)}} \ostate{11}}    \\
    OT'_5 & = \openrule
             {1 \xrightarrow{r}_{C_5} 1,\\\{\xrightarrow{b3}_R\}
             	}
             {\ostate{11} \xrightarrow{b3} \ostate{11}}
    \end{eqnarray*}
  \end{minipage}
%  \label{schema:enable5}
\end{figure}

@@

       	\inferrule*[myfraction=\reddottedrule]
       	{\{s^1_i\xrightarrow{a_i}_i {s^{1}}'_i\}^{i\in I_1}, % , s^1_i,s^{1'}_i\in
       		%States(I_1)
       		\{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
       	{s^1 \xrightarrow {v} {s^{1}}'}

@@

       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\inferrule*[myfraction=\reddottedrule]
       	{\{s^{2}_{pi}\xrightarrow{a_{p i x}}_i s^{2}_{p i x}\}^{i\in I_{2 p x}},
       		\{\xrightarrow{b_{j p x}}_j\}^{j\in J_{2px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
       	{s^2_p \xrightarrow {v_{px}} s^{2}_{px}}
       	%         \right)
       	\end{mathpar}

@@

       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\inferrule*[myfraction=\reddottedrule]
       	{\{s^{3}_i\xrightarrow{a_{i p x y}}_i s^{3}_{i p x y}\}^{i\in I_{3 p x y}},
       		\{\xrightarrow{b_{j p x y}}_j\}^{j\in J_{3pxy}}, 
       		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
       	{s^3 \xrightarrow {v_{pxy}} s^{3}_{pxy}}
       	%         \right)

@@

	\centerline{
		$\openrule
		{0 \xrightarrow{a}_{gw2} 2 \\
			\xrightarrow{b}_{P21}
			\\ \sm{Pred}_{Root} \\ \emptyset}
		{\ostate{000} \xrightarrow{v} \ostate{020}}
		$
	}

@@

\begin{mathpar}
     \openrule
         {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad
           2 \xrightarrow{bm(tgt2_2)}_{gw2} 0 \quad
           \xrightarrow{b}_{P3}
           \quad Pred_{Root}}
         {\ostate{020} \xrightarrow{v} \ostate{100}}
\end{mathpar}
with
$Pred_{Root} = [tgt1_1=tgt2_2 \land b=um(tgt2_2) \land
  b\in \Sort_{P3} \land v = \underline{bm(tgt2_2)}]  $

>>>>

The semantics of open pNets will be defined  as an open automaton. An open
automaton is an automaton where each transition composes transitions of several LTSs with
action of some holes, the transition occurs if some predicates hold, and can involve a 
set of state modifications.
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transitions]
	\label{def:OpenTransitions}
	An \emph{open transition} over a set  $(S_i,s_{0 i}, \rightarrow_i)^{i\in
	I}$ of LTSs, a
	set $J$ of holes with sorts $\Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is 
	a structure of the form:	
	\begin{mathpar}
	\inferrule*[myfraction=\reddottedrule]
	{\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred, \Post}
	{s \OTarrow {v}s'}
	\end{mathpar}
	Where $s, s'\in\mathcal{S}$ and for all
        $i\in I$, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the
	LTS $(S_i,s_{0 i}, \rightarrow_i)$, and $\xrightarrow{b_j}_j$
        is a transition of the hole $j$, for any action $b_j$ in the
        sort $\Sort_j$. $v$ is a variable denoting the resulting action
        of this open transition. \Pred\ is a predicate 
	over the different variables of the
	terms, labels, and states $s_i$, $b_j$, $s$, $v$. \Post\ is a set of equations that 
	hold \emph{after the open transition}, they are represented as a substitution of the 
	form $\{x_k\gets e_k\}^{k\in K}$ 
	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
	variables of the open transition.
\end{definition}

@@

 \smallskip
 $  OT_2  = \openrule{
                       0 \xrightarrow{\delta}_{C_3} 1 ~~
                            0 \xrightarrow{l}_{C_4} 0  ~~                 
                            \xrightarrow{\delta(x4)}_P ~~
                            \xrightarrow{accept(x4)}_Q 
                      }
  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
    {A1_0 \OTarrow{\underline{\delta(x4)}} A1_1}
  $
\end{example}

@@

	\begin{description}
		\item[{\bf Tr1:}]
		$\inferrule
		{ s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
					J}\rangle} s'\in \to  }
		{ \mylangle  S,s_0, \to \myrangle
			\models
			\inferrule*[myfraction=\reddottedrule]
			{\{s \xrightarrow{\alpha}_p s'\} ,\emptyset ,
			e_b,\left\{x_j\gets e_j\right\}^{j\in J}}
			{\ostate{s} \OTarrow{\alpha} \ostate{s'}}
		}
		$
	\end{description}
%	Note that this note is greatly simplified by the fact that variables are local to 
%	thread; introducing global state variables or accepting loops to the same 
%	state would 
%	require to reason 
%	on the scope of 
%	each variables, and to introduce additional variables to handle the several occurence 
%	of the same pLTS variable in the predicates. Indeed the constraints on pLTS 
%	transitions 
%	ensure that the same variable never appears both on the left and on the right of the 
%	equations of a predicate.

@@

	\noindent
    $\inferrule
    {k\!\in\! K \\ SV\!\!= \!{\tt clone}(SV_k) \!=\! \alpha_m^{m \in I_k\uplus J_k} \!\to\! 
    \alpha'_k \\
    	Leaves(p) \!=\! \pLTS_l^{l\in L} \\    	
    	\forall m\in I_k.
    	\pNet_m \models
    	\inferrule*[myfraction=\reddottedrule]
    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}}
    	%\land
    	%Leaves(\pNet_m) = \overline{pLTS}^{L_k})
    	\\
    	I' = \biguplus_{m\in I_k}\!\! I_m'
    	\\ J' = \biguplus_{m\in I_k}\!\! J'_m \uplus J_k 	\\
    	\Pred = \bigwedge_{m\in I_k}\!\! \Pred_m \land
    	\Pred_{\symb{sv}}(SV,a_i^{i\in I_k},b_j^{j\in J_k},v)\\
    	\forall j\!\!\in\!\! J_k. {\tt 
    		fresh}(b_j) \\ {\tt fresh}(v) \\ 
    	\forall i\in
    	L\backslash I'.\,s'_i=s_i 
    }
    {\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\inferrule*[myfraction=\reddottedrule]
    		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I^\prime},
    		\{\xrightarrow{b_j}_j\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_k} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {v}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
    $

@@

\begin{figure}[tb]
\begin{mathpar}
  \small
  \inferrule
    {\inferrule
        {0 \xrightarrow {\delta}_{C_3} 1}
        {C_3
          \models
            \openrule{
              0 \xrightarrow {\delta}_{C_3} 1,\,
              \{\xrightarrow{\delta(x_1)}_P\},\,
              v_1=\delta(x_1)}
                      {\ostate{0}\OTarrow{v_1}\ostate{1}}
        }\\
%      \sm{fresh}v         \\
      \inferrule%*[right={L_1}]
        {
%          \sm{fresh}{a_Q} \\
          \inferrule
              {0 \xrightarrow{l}_{C_4} 0}
              % {\ostate{0}\xrightarrow{l}\ostate{0}}
              {C_4
                \models
                \openrule{
                      0 \xrightarrow l_{C_4} 0,\,
                      \sm{Pred}_{C_4}}
                      {\ostate{0}\OTarrow{l}\ostate{0}}
              }
        }
        {
          \textrm{Q>>R}\models
              \openrule
                  { 0 \xrightarrow {l}_{C_4} 0,\,
                    \{\xrightarrow{acc(x_2)}_Q\},\,
                    \ v_2=acc(x_2)
                  }
                  {\ostate{0}\OTarrow{v_2}\ostate{0}}
        }   
    }
    {
     \textrm{P>>(Q>>R)}
     \models
     \openrule
         { 0 \xrightarrow{\delta}_{C_3} 1, \\ 0 \xrightarrow{l}_{C_4} 0,\\
           \{\xrightarrow{\delta(x)}_P,\,\xrightarrow{acc(x)}_Q\}, \\
            a_3=v_1 \wedge v=a_3 \wedge x_1=x_2
           }
         {\ostate{00} \OTarrow{v} \ostate{10}}
      }\vspace{-4ex}
\end{mathpar}
  \caption{Proof of transition $OT_2$ (with interaction of processes $P$ and $Q$) for ``P>>(Q>>R)''}
  \label{usingrules:OT2}
\end{figure}

@@

 \begin{itemize}
 \item  For any open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \inferrule*[myfraction=\reddottedrule]
         {\{s^1_i\xrightarrow{a_i}_i s^{1'}_i\}^{i\in I_1}, % , s^1_i,s^{1'}_i\in 
         %States(I_1)
           \{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s^1 \OTarrow {v} s^{1'}}

\end{mathpar}
 there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
 \begin{mathpar}
%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
    \inferrule*[myfraction=\reddottedrule]
         {\{s^{2}_i\xrightarrow{a_{i x}}_i s^{2}_{i x}\}^{i\in I_{2 x}},
           \{\xrightarrow{b_{j x}}_j\}^{j\in J_{2x}}, \Pred_{OT_x},\Post_{OT_x}}
         {s^2 \OTarrow {v_x} s^{2}_x}
%         \right)
\end{mathpar}
 such that  $\forall x, J_1=J_{2x}, (s^{1'},s^{2}_x|\Pred_{s^{1'},s^{2}_x})\in 
 \mathcal{R}$; 
 and  \\
 $\Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j. b_j=b_{jx}  \Rightarrow \Pred_{OT_x}
     \land v\!=\!v_x \land  
     \Pred_{s^{1'},s^{2}_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
     %     \right)$.

@@

 \begin{mathpar}
 \inferrule*[myfraction=\reddottedrule]
         {\{s_i\xrightarrow{a_i}_i s'_i\}^{i\in I_1}, 
           \{\xrightarrow{b_j}_j\}^{j\in J},\Pred,\Post}
         {s \OTWeakarrow {v} s'}
         \in \mathcal{T}^*
 \end{mathpar}

@@

 \begin{itemize}
 \item  For any open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \inferrule*[myfraction=\reddottedrule]
         {\{s^1_i\xrightarrow{a_i}_i s^{1'}_i\}^{i\in I_1},
           \{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s^1 \OTarrow {v} s^{1'}}

\end{mathpar}
 there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2^*$:
 \begin{mathpar}
    \inferrule*[myfraction=\reddottedrule]
         {\{s^{2}_i\xrightarrow{a_{i x}}_i s^{2}_{i x}\}^{i\in I_{2 x}},
           \{\xrightarrow{b_{j x}}_j\}^{j\in J_{2x}}, \Pred_{OT_x},\Post_{OT_x}}
         {s^2 \OTWeakarrow {v_x} s^{2'}_x}
\end{mathpar}
 such that  $\forall x, J_1=J_{2x}, (s^{1'},s^{2'}_x|\Pred_{s^{1'},s^{2'}_x})\in \mathcal{R}$; 
 and  \\
 $\Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j. b_j=b_{jx}  \Rightarrow \Pred_{OT_x}
     \land v\!=\!v_x \land  
     \Pred_{s^{1'},s^{2'}_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$

@@

\begin{figure}[h]
  \begin{minipage}{2cm}
  \includegraphics[width=\linewidth]{XFIG/PQR-automaton}
  \end{minipage}
  \hspace{10mm}
  \begin{minipage}{7cm}
  \begin{eqnarray*}
    OT_1 & = \openrule{0 \xrightarrow{l}_{C_3} 0
    	\\\xrightarrow{a1}_P\\ a1\neq\delta(x)}
    {\ostate{00} \OTarrow{a1} \ostate{00}}\\
    OT_2 & = \openrule{
                       0 \xrightarrow{\delta}_{C_3} 1, ~~
                            0 \xrightarrow{l}_{C_4} 0,  ~~                 
                            \{\xrightarrow{\delta(x1)}_P, ~~
                            \xrightarrow{acc(x1)}_Q\}
                      }
                      {\ostate{00} \OTarrow{\underline{\delta(x1)}} \ostate{10}}    \\
    OT_3 & = \openrule{0 \xrightarrow{l}_{C_4} 0,
                        \\1 \xrightarrow{r}_{C_3} 1,\\
                        \xrightarrow{a2}_Q,\\a2\neq\delta(x)
                        }
    {\ostate{10} \OTarrow{a2} \ostate{10}}\\
    OT_4 & = \openrule{
                       0 \xrightarrow{\delta}_{C_4} 1, \qquad
                       1 \xrightarrow{r}_{C_3} 1, \qquad
                       \{\xrightarrow{\delta(x2)}_Q, \qquad 
                       \xrightarrow{acc(x2)}_R\} 
                       }
                      {\ostate{10} \OTarrow{\underline{\delta(x2)}} \ostate{11}}    \\
    OT_5 & = \openrule{1 \xrightarrow{r}_{C_3} 1, \\1 \xrightarrow{r}_{C_4} 1, 
    	\\\xrightarrow{a3}_R
    	}
    {\ostate{11} \OTarrow{a3} \ostate{11}}
    \end{eqnarray*}
  \end{minipage}
  \caption{Open Automaton for the term ``P>>(Q>>R)''}
  \label{schema:enable3bis}
\end{figure}

\begin{figure}[t]
  \begin{minipage}{2cm}
  \includegraphics[width=\linewidth]{XFIG/PQR2-automaton}
  \end{minipage}
  \hspace{10mm}
  \begin{minipage}{7cm}
  \begin{eqnarray*}
    OT'_1 & = \openrule
             {
               0 \xrightarrow{l}_{C_3} 0,~~0 \xrightarrow{l}_{C_4} 0,~~
               \{\xrightarrow{b1}_P\},~~ b1\neq\delta(y)
               }
             {\ostate{00} \OTarrow{b1} \ostate{00}}\\
    OT'_2 & = \openrule
             {
                       0 \xrightarrow{l}_{C_5} 0, ~~
                       0 \xrightarrow{\delta}_{C_6} 1,  ~~
              \{\xrightarrow{\delta(y1)}_P,~~      \xrightarrow{acc(y1)}_Q\}~~ 
                      }
             {\ostate{00} \OTarrow{\underline{\delta(y1)}} \ostate{01}}\\
    OT'_3 & = \openrule
             {
               0 \xrightarrow{l}_{C_5} 0,\\0 \xrightarrow{r}_{C_6} 0,
               \\ \{\xrightarrow{b2}_Q\},\\b2\neq\delta(y)
               }
    {\ostate{01} \OTarrow{b2} \ostate{01}}\\
    OT'_4 & = \openrule
             {
                       0 \xrightarrow{\delta}_{C_5} 1, ~~
                       1 \xrightarrow{r}_{C_6} 1, ~~\{\xrightarrow{\delta(y2)}_Q, ~~
                    \xrightarrow{accept(y2)}_R\} 
                                 }
             {\ostate{01} \OTarrow{\underline{\delta(y2)}} \ostate{11}}    \\
    OT'_5 & = \openrule
             {1 \xrightarrow{r}_{C_5} 1,\\\{\xrightarrow{b3}_R\}
             	}
             {\ostate{11} \OTarrow{b3} \ostate{11}}
    \end{eqnarray*}
  \end{minipage}
%  \label{schema:enable5}
\end{figure}

@@

       	\inferrule*[myfraction=\reddottedrule]
       	{\{s^1_i\xrightarrow{a_i}_i {s^{1}}'_i\}^{i\in I_1}, % , s^1_i,s^{1'}_i\in
       		%States(I_1)
       		\{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
       	{s^1 \OTarrow {v} {s^{1}}'}

@@

       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\inferrule*[myfraction=\reddottedrule]
       	{\{s^{2}_{pi}\xrightarrow{a_{p i x}}_i s^{2}_{p i x}\}^{i\in I_{2 p x}},
       		\{\xrightarrow{b_{j p x}}_j\}^{j\in J_{2px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
       	{s^2_p \OTarrow {v_{px}} s^{2}_{px}}
       	%         \right)
       	\end{mathpar}

@@

       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\inferrule*[myfraction=\reddottedrule]
       	{\{s^{3}_i\xrightarrow{a_{i p x y}}_i s^{3}_{i p x y}\}^{i\in I_{3 p x y}},
       		\{\xrightarrow{b_{j p x y}}_j\}^{j\in J_{3pxy}}, 
       		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
       	{s^3 \OTarrow {v_{pxy}} s^{3}_{pxy}}
       	%         \right)

@@

	\centerline{
		$\openrule
		{0 \xrightarrow{a}_{gw2} 2 \\
			\xrightarrow{b}_{P21}
			\\ \sm{Pred}_{Root} \\ \emptyset}
		{\ostate{000} \OTarrow{v} \ostate{020}}
		$
	}

@@

\begin{mathpar}
     \openrule
         {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad
           2 \xrightarrow{bm(tgt2_2)}_{gw2} 0 \quad
           \xrightarrow{b}_{P3}
           \quad Pred_{Root}}
         {\ostate{020} \OTarrow{v} \ostate{100}}
\end{mathpar}
with
$Pred_{Root} = [tgt1_1=tgt2_2 \land b=um(tgt2_2) \land
  b\in \Sort_{P3} \land v = \underline{bm(tgt2_2)}]  $
